\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{url}

\usepackage{a4wide}
\usepackage{longtable}           % lange Tabellen
%\usepackage[dvips]{epsfig}

\usepackage{fancyhdr}
\pagestyle{fancy}
%\fancyhf{}                              % bisherige Kopf- und Fusszeilen loeschen
\fancyhead[R]{Nico Schottelius}            % rechter Kopfzeileneintrag
%\fancyhead[L]{Projekdokumentation}      % linker Kopfzeileneintrag
%\fancyhead[L]{\thepage}      % linker Kopfzeileneintrag
%\fancyfoot[C]{\thepage}                % Fusszeileneintrag (Seitenzahl zentriert)
\renewcommand{\headrulewidth}{0.4pt}  % Strichstaerke unter der Kopfzeile
% ----------------------------------------------------------------------------
% let's start
\begin{document}
\title{Development of a secure, peer-to-peer, decentralised anonymous chat system}
\date{\today}
\author{Nico Schottelius (nico-hsz-t (o) schottelius.org)}
% ----------------------------------------------------------------------------
\maketitle
\newpage
% ----------------------------------------------------------------------------
% Inhaltsverzeichnis
\tableofcontents
\listoftables
%\listoffigures
\newpage

% ----------------------------------------------------------------------------
\section{Introduction}

Anonymous communication networks were first intro-
duced by David Chaum in his seminal paper [10] describing
the mix as a fundamental building block for anonymity.
(aus tor2)

\subsection{Abstract}
hier oder weiter oben? - siehe lisa vortrag!

\subsection{Abbreviations}
\subsection{Starting Position}
local, skype, untrustworthy

\subsection{Motivation}
From EBS + EOF

\subsection{Objectives}
From EOF + Latency "`low"', eventual consistency
\subsubsection{Steganographic}
Not for hiding, but to support longer überleben?
http is pretty well suited for this.
mixing with smtp, imap, pop3, tcp. etc.

% ----------------------------------------------------------------------------
\section{Related work/Alternatives/Existing solutions}
\subsection{IRC+SSL}
\subsection{SILC}
\subsection{Onion Routing}
\subsection{Tor}
\subsection{Comparison}
All the solutions with objectives.
\subsection{Conclusions}
Latency, http/ssh vs. email

% ----------------------------------------------------------------------------
\section{System Design}
The theory behind EOF.
Search for documents proving/supporting the idea.

Different programs handle different objectives
\subsection{Use objectives and derive}
\subsection{Objective 1 ...}
\subsection{Additional constraints}
Cross-OS. Posix and/or ansi-c. ui changable.
\subsection{Key Exchange}
Not implemented, manually.
% ----------------------------------------------------------------------------
\section{Intra Machine Intra Program Protocol}
\subsection{Interfaces}
Sockets, Environment, Paths, etc.
\subsection{Data Types}
\subsection{Sub Programs}
Consists of the following sub-programs:
encryption, dictionary, key/peer exchange daemon (if possible in this work),
% ----------------------------------------------------------------------------
\section{Sub Programs}
Describe what it does, how it does and where it is implemented.
\subsection{Noise / Dictionary / Database}
Generate input for times when there is no user input.
Random or db or or or.
Networt traffic
\subsection{Encryption}
Splitting of encryption into a seperate program can make use of
multiple computing ressources.
\subsection{User Interface}
Own program, indepentend of core.
\subsection{Transports}
Receive/Send

% ----------------------------------------------------------------------------
\section{Inter Machine Protocol}
On the "`wire"'. Different transports. Constant transport.
Define name (postcard?!) here. Includes transport specific
header / meta information.

\subsection{Variable Transports}
Different transports for one peer.
\subsection{List of Supported Transports}
To ensure interoperability, clients which support a specific
protocol version must support all listed transport protocols.
\begin{longtable}{|c|c|c|}
\caption{Transport protocols}\\
\hline
\textbf{Protocol} & \textbf{Description} & \textbf{Supported versions}\\
\hline
tcp & Transmission Control Protocol & 0.1 - 0.1\\
\hline
\end{longtable}

\subsection{Variable Peers}
Different routes for every packet
\subsection{Constant sending}

\subsection{Source based routing}
Either here or in Intra Machine Intra Client
\subsection{Peer selection}
Which peers, how many. Constant? May give upper bounds of latency.

8 * 0.5seconds = 4 seconds delay.

\subsection{Bandwidth usage}
\begin{verbatim}
>>> messages_size=4*1024
>>> messages_per_second=4
>>> bytes_per_second=messages_per_second*messages_size
>>> print(bytes_per_second)
16384
>>> bytes_per_day=86400*bytes_per_second
>>> print(bytes_per_day)
1415577600
>>> print(bytes_per_day/1024**2)
1350.0
>>> bytes_per_month=month_length*bytes_per_day
>>> print(bytes_per_month/1024**2)
41062.5
>>> print(bytes_per_month/1024**3)
40.10009765625
\end{verbatim}
16 KiB/s or 128 KBit/s, 2 ISDN lines. Around 1.4 GiB per day or
circa 40 GiB per month.

% ----------------------------------------------------------------------------
\section{Inter Machine Inter Program Protocol}
After decoding the received packet. Forward, etc.
Based on part os EOF simple data types.
\subsection{Message types}
List of messages here
\subsection{Message 1}
description here

% ----------------------------------------------------------------------------
\section{Implementation}
This section describes the actual implementation
Python?
\subsection{Non-Cross OS Support}
Support for different OS would have made development more
hard, so support for POSIX alike operating systems was targeted.

\subsection{Python-GPG}
Various implementations \cite{python-gpg}
PyMe: 3 Nachrichten in 2010
\url{http://sourceforge.net/mailarchive/forum.php?forum_name=pyme-help&style=threaded}

python-gnupg commits in september 2011 \cite{python-gnupg}

%\input{titel.tex}                   % done
%\input{erklaerung.tex}              % done
% ----------------------------------------------------------------------------
\input{conclusions}
% ----------------------------------------------------------------------------
\input{appendix.tex}
\input{sources.tex}
% ----------------------------------------------------------------------------
\end{document}
